\newpage
\chapter*{Thanks for taking part!}
\addcontentsline{toc}{chapter}{Thanks for taking part!}

Do you want to know more? Of course you do! \citet{fried-12} has developed a number of tutorials suitable for the beginner wishing to learn more about the \gls{Arduino} system. These tutorials can be accessed at the following URI: http://www.ladyada.net/learn/arduino/

Would you like to work on or with technology like this in the future? Would you like to change profession? Then you might also be interested in investigating the newly formed \textit{Internet of Things} degree course being run at the Waterford Insstitute of Technology: https://www.wit.ie/courses/school/science/department\_of\_computing\_maths\_physics/bsc-hons-in-the-internet-of-things

I hope you enjoyed this workshop and your time spent here. The South East Makerspace has developed several workshops in the IoT space and hope to continue creating more in the future. Be sure to sign up to the mailing list, and follow us on social media to keep informed about our events and workshops! We would be delighted to welcome new faces, however full membership is only open to those over 18 years old (insurance reasons)! For information on SEMS see:

\begin{description}
	\item[Facebook] http://www.facebook.com/SouthEastMakerSpace
	\item[FAQ] https://wiki.southeastmakerspace.org/faq
	\item[Google+] http://plus.google.com/u/0/108025738894009906004/
	\item[How to join] https://wiki.southeastmakerspace.org/how\_to\_join\_sems
	\item[Mailing List] http://lists.southeastmakerspace.org/mailman/listinfo/sems-general
	\item[Secure Contact] https://www.southeastmakerspace.org/contact
	\item[Twitter] http://twitter.com/SEMakerSpace
\end{description} 




